The K2 Halo Photometry Campaign

### 2019-04-03 paper/ms.tex
figures

\begin{figure*}
\plotone{../release/c14/hlsp_halo_k2_llc_200182931_-c14_kepler_v1_lc.pdf}
\end{figure*}

>>>>

\begin{figure*}
\plotone{../release/c14/hlsp_halo_k2_llc_200182931_-c14_kepler_v1_lc.pdf}
\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for $\rho$~Leonis.}
\end{figure*}

\begin{figure*}
\plottwo{lag_lc_cdpp.pdf}{lag_sc.pdf}
\caption{Behaviour of long cadence (left) and short cadence (right) CDPP as a function of lag parameter $l$. For long cadence this shows a minimum for L1 norm and $l=10$, i.e. for objective function $\Lambda_{1,10}$. For short cadence CDPP continuously improves for higher lags and shows no strong differences between L1, L2 or~L3 norms.}
\end{figure*}
